Open Set Logo Detection and Retrieval

### 2017-09-06 paper-review.tex
Reworked section 3. Added open set figure.

% --| My Acronyms |---------------------------------------------------
\newacro{CNN}{Convolutional Neural Network}
\newacro{CRF}{Conditional Random Field}
\newacro{FCN}{Fully Convolutional Neural Network}
\newacro{FROC}{Free-Response Receiver Operating Characteristic}
\newacro{GMM}{Gaussian Mixture Model}
\newacro{HOG}{Histogram of Oriented Gradients}
\newacro{LitW}{Logos in the Wild}
\newacro{PCA}{Principle Component Analysis}
\newacro{SIFT}{Scale Invariant Feature Transform}
\newacro{SVM}{Support Vector Machine}

@@

\begin{document}

@@

\abstract{
%%TODO write text here, 70-200 words
Current logo retrieval research focuses on closed set scenarios. We argue that the logo domain is too large for this strategy and requires an open set approach. To foster research in this direction, the large-scale Logos in the Wild dataset is collected and released to the public.
Searching for logos in image data has many applications, with judging the effectiveness of advertisement in sports event broadcasts being one example. Given a query sample in shape of a logo image, the task is to find all further occurrences of this logo in a database of images or videos. Currently, common logo retrieval approaches are unsuitable for this task because of their closed world assumption. To address this issue, an open set logo retrieval method is proposed in this work which allows search for previously unfamiliar logos only by one query sample. A two stage concept with an open set logo detection and comparison is proposed. Both modules are based on task specific \acp{CNN}. The novel Logos in the Wild dataset serves to train the modules with sufficient appropriate in-the-wild data. 
The proposed method extends the application field in comparison to closed set approaches and significant improvements over baseline methods derived from these state-of-the-art closed set approaches are shown. 
}

@@

% Detector Frameworks: Faster R-CNN~\cite{ren2015}, SSD~\cite{liu2016b}, Yolo~\cite{redmon2016}, ...
\subsection{Object Detector Frameworks}
Early detectors applied hand-crafted features, such as Haar-like features, combined with a classifier to detect objects in images \cite{viola2004}. 
Nowadays, deep learning methods surpass the traditional methods by a significant margin. In addition, they allow a certain level of object classification within the detector which is mostly used to simultaneously detect different object categories \cite{sermanet2013}. 
%The OverFeat framework uses sliding windows on multiple scales of the image and combines the \ac{CNN} features to detect objects and classify them. 
The YOLO detector \cite{redmon2015} introduces an end-to-end network for object detection and classification based on bounding box regressors for object localization. This concept is similarly applied by the Single Shot MultiBox Detector (SSD) \cite{liu2015}. 
Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a region proposal network (RPN) to detect object candidates in the feature maps and classifies the candidate regions by a fully connected network. 
Improvements of the Faster R-CNN are the Region-based Fully Convolutional Network (R-FCN) \cite{jifengdai2016b}, which reduces inference time by an end-to-end fully convolutional network, and the Mask R-CNN \cite{he2017}, adding a classification mask for instance segmentation.
%
\begin{figure*}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 5cm 0cm 0cm, clip]{img/openset.pdf}%
\caption{Comparison of closed and open set logo retrieval strategy.}%
\label{fig:openClosedSet}
\end{figure*}%

@@

\section{\uppercase{Logo Detection}}
%\noindent- class agnostic detector \\
%- different base networks: VGG-CNN-M, VGG16
\noindent The current state-of-the-art approach for scene retrieval is to create a global feature of the input image. This is achieved either by inferring from the complete image or by searching for key regions and then extracting features from the located regions, which are finally fused into a global feature. For logo retrieval, extraction of a global feature is counterproductive because it lacks discriminative power to retrieve small objects. Additionally, global features usually include no information about the size and location of the objects which is also an important factor for logo retrieval.

Therefore, we chose a two-stage approach consisting of logo detection and logo classification as illustrated in figure~\ref{fig:pipeline}. First, the logos have to be detected in the input image. 
There are a lot of options to search for objects. We utilized Faster R-CNN network to detect logos in images, proposed by Girshick et al. \cite{ren2015}. It made the selection of an appropriate baseline method easier, since currently almost only Faster R-CNNs are used in the context of logo retrieval. Nevertheless, these solutions are not suitable to detect logos in an open-set manner, by considering only the class probability distribution. Therefore, the task raises the need for a generic logo detector, which is able to detect every kind of logos.
During the training of a Faster R-CNN, a Region Proposal Network will be trained to detect all the objects, which it was trained on. It provides a decision whether a region of the image is a logo or not. The trained RPN and the underlying feature extractor network can be extracted and employed as a universal detector. 
Another option to detect logos is a class agnostic Faster R-CNN, which is trained with two classes: background and logo. We argue, that this solution yields better performance than the RPN detector because of two reasons. Firstly, because of the fully connected layers preceding the final classifier serving a strong classification power and the bounding box regression layers, making further bounding box adjustments. Secondly, the combination of RPN and the FC classifier shape a cascade of detectors, similarly as in \cite{viola2004}, where the RPN counts for a weaker classifier, which is faster and allowing more false positives. For the combination it is expected to have a lower false positive rate.

@@

\section{\uppercase{Logo Comparison}}
%TODO write text here
After a logo is detected in an image, a correspondence from the query set should be searched. In order to retrieve as much objects from the images as possible, the detectors should work with a high recall. Although, for difficult tasks like open-set logo detection, high recall values induce usually a lot of false positive possible object locations. These examples should be eliminated by appropriate classifier. However, in case of image retrieval the goal is not direct classification, but rather feature extraction of a found region. Thus, the features of the logos of all the query images and the search set should be collected. The retrieved feature vectors are then normalized and the similarities of them are calculated with cosine similarity.
For baseline method, a Faster R-CNN is utilized, trained as usual. During inference, instead of detecting and classifying directly from the class probabilities, first the logos will be detected by processing the output of the RPN. Then, the class scores are used as discriminative feature for the underlying region. The feature vector of the query images are extracted from the complete image, since the logos fill the majority of these images.
Donahue et al. proposed \cite{donahue2015}, that convolutional networks can produce excellent descriptors of the input image, regardless of the absence of fine-tuning to the specific context of the image. For this purpose, a network is pretrained on very large datasets, after which it can be deployed for a broad set of computer vision problems. In our case, the networks were additionally fine-tuned with different amount of logo images.
The proposed logo retrieval system consists of a class agnostic logo detector and a feature extractor network. This setup is advantageous for the quality of the extracted features, because the complete network is only focused on a specific region.

@@

The collected Logos in the Wild dataset exceeds the size of all related logo datasets as shown in table~\ref{tab:logoDatasets}. Even the union of all related logo datasets contains significantly less brands and RoIs which makes Logos in the Wild a valuable large-scale dataset.
 %Table~\ref{tab:datasetStatistics} gives more details.
The annotation is still an ongoing process and further larger versions of the dataset are expected to be published in the future (??).
%
%Potential uses: 
%In this work, the dataset is mainly used for training purposes
%In addition to the simple use as training data,

@@

In all cases the \acp{CNN} are trained until convergence which requires ?? to ??k iterations with a batch-size of ??. Training duration depends on the architecture as well as the amount of training data.
%TODO write text here

\subsection{Detection}
%- train 3 different detectors: multi-class Faster R-CNN (maybe RPN), single-class Faster R-CNN, single-class Faster R-CNN + own logos\\
%- test on FlickrLogos-32 => FROC plot\\
%- test first two detectors on own logo dataset => FROC plot\\
%- Example Detections\\
%%TODO write text here
As baseline, the state-of-the-art closed set logo retrieval method from~\cite{su2016} based on Faster R-CNN is employed and trained on the public portion of the training data.
It is naively adapted to open set detection by using the RPN scores as detections. This skips the closed set classification part of the network which is trained on different logos than should be detected on the test set.
%Because of the closed set training strategy, only brands occurring in the training set are the final outcome of this detector. 
%Adaptation to open set detection of previously unseen logos is achieved by using the RPN scores before classification as detections.
%Because of the strict separation of train and test brands, and the closed set training strategy
%the RPN scores serve as detections.
The proposed logo detector is first trained on the same public data for comparison. The results in figure~\ref{fig:detectionFroc} indicate that this strategy is superior by a significant margin. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
\caption{Detection FROC curves for FlickrLogos-32 test set.}%
\label{fig:detectionFroc}
\end{figure}%
%

@@

\subsubsection*{FlickrLogos-32}
\vspace*{-2.5mm}
In 10 iterations, each of the 10 FlickrLogos-32 train samples for each brand serves as query sample. This allows to assess the statistical significance of results similar to a 10-fold-cross-validation strategy. Figure~\ref{fig:classificationFroc} shows the FROC results for the trained networks including indicators for the standard deviation of the measurements. The detection identification rate denotes the amount of ground truth logos which are correctly detected and are assigned the correct brand.
While the baseline method is only able to find a minor amount of the logos, our best performing approach is able to correctly retrieve 25 percent of the logos if tolerating only one false alarm every 100 images.
As expected, the more recent network architectures provide better results. Also, including the \ac{LitW} data in the training yields a significant boost in performance. Specifically, the larger training dataset has a larger impact on the performance than a better network architecture. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 7cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
\caption{Detection+Classification FROC curves for FlickrLogos-32 test set. Including dashed indicators for one standard deviation. DenseNet results are omitted for clarity, refer to table~\ref{tab:mapFlickr} for full results.}%
\label{fig:classificationFroc}
\end{figure}%
%
%As far as we are aware, this is the first experiment with open set logo retrieval on 
Table~\ref{tab:mapFlickr} compares our open set results with closed set results from the literature in terms of the mean average precision (\map). 
%
\begin{table}[t]
\centering
\begingroup	
\setlength{\tabcolsep}{6pt}
\caption{FlickrLogos-32 test set retrieval results.}
\label{tab:mapFlickr}
\begin{small}
% Table generated by Excel2LaTeX from sheet 'FlickrLogos-32Test'
\begin{tabular}{crc}
\textbf{setting} & \multicolumn{1}{c}{\textbf{method}} & \textbf{\map} \bigstrut[b]\\
\hline
\multirow{7}[2]{*}{\begin{sideways}open set\end{sideways}} & baseline, public~\cite{su2016} & 0.036 \bigstrut[t]\\
      & \textit{VGG16, public} & 0.286 \\
      & \textit{ResNet101, public} & 0.327 \\
      & \textit{DenseNet161, public} & 0.368 \\
\cline{2-3}      
      & \textit{VGG16, public+\ac{LitW}} & 0.382 \bigstrut[t]\\
      & \textit{ResNet101, public+\ac{LitW}} & \textbf{0.464} \\
      & \textit{DenseNet161, public+\ac{LitW}} & 0.448  \bigstrut[b]\\      
\hline
\multirow{4}[1]{*}{\begin{sideways}closed set\end{sideways}} & BD-FRCN-M \cite{oliveira2016} & 0.735 \bigstrut[t]\\	
      & DeepLogo \cite{iandola2015} & 0.744 \\ 
      & Faster-RCNN \cite{su2016} & 0.811 \\
      & Fast-M \cite{bao2016} & \textbf{0.842} \\
\end{tabular}%
\end{small}
\endgroup
\end{table}
We achieve more than half of the closed set performance in terms of \map~with only one sample for a brand at test time instead of dozens or hundreds of brand samples at training time. In addition, our approach is not limited to the 32 FlickrLogos brands but generalizes with a similar performance to further brands. In contrast, the closed-set approaches hardly generalize as is shown by the baseline open set method. This is the second best closed set approach only retrained on out-of-test brands.

\subsubsection*{SportsLogos}
\vspace*{-2.5mm}
In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events. In total, this SportsLogos test set includes 298 annotated frames with 2,348 logos of 40 brands. In comparison to public logo datasets, the logos are usually significantly smaller in these cases and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}. Besides perimeter advertising, logos on clothing or equipment of the athletes and TV station or program overlays are the most occurring logo types.
Overall, the results in this application scenario are slightly worse than in the FlickrLogos-32 benchmark with a drop in \map~from 0.464 to 0.354 for the best performing method, as indicated in figure~\ref{fig:classificationFrocFootball}. The baseline approach takes the largest performance hit showing that closed set approaches not only generalize badly to unseen logos but also to novel domains. In contrast, the proposed open set strategy shows a relatively stable cross-domain performance. Training with \ac{LitW} data again improves the results significantly.
%
\begin{figure*}%
\centering%
\includegraphics[width=\linewidth]{img/football-1908719_1920_cut.jpg}%
\caption{Example football scene with small logos in the perimeter advertising.}%
\label{fig:footballSample}
\end{figure*}%
%
%Due to copyright reasons this internal dataset cannot be made publicly available.
%
%\begin{table}[t]
%\centering
%\begingroup	
%\setlength{\tabcolsep}{5pt}
%\caption{SportsLogos dataset statistics.}
%\label{tab:sportDataStatistics}
%\begin{small}
%\begin{tabular}{l|cccc}
% & \textbf{phase} & \textbf{brands} & \sizebox{1.0cm}{\textbf{logo images}} & \textbf{RoIs} \bigstrut[b]\\
%\hline
%football-1 & \multirow{3}{*}{train} & {104} & {331} & {3,329} \bigstrut[t]\\
%{ski} & & {27} & {179} & {701} \\
%{ice hockey} & & {19} & {410} & {3,920} \bigstrut[b]\\
%\hline
%{football-2} & test & 40 & 298 & 2,348 \bigstrut\\
%%\hline
%%{total} & & {143 (union)} & {1,218} & {10,298} \bigstrut[t]\\
%\end{tabular}
%\end{small}
%\endgroup
%\end{table}
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 8cm 0cm 0cm, clip]{img/classificationFrocFootball.pdf}%
\caption{Detection+Classification FROC curve for SportsLogos test set. \map~is given in brackets.}%
\label{fig:classificationFrocFootball}
\end{figure}%
%

>>>>

% --| My Acronyms |---------------------------------------------------
\newacro{CNN}{Convolutional Neural Network}
\newacro{CRF}{Conditional Random Field}
\newacro{FCN}{Fully Convolutional Neural Network}
\newacro{FROC}{Free-Response Receiver Operating Characteristic}
\newacro{GMM}{Gaussian Mixture Model}
\newacro{HOG}{Histogram of Oriented Gradients}
\newacro{LitW}{Logos in the Wild}
\newacro{PCA}{Principle Component Analysis}
\newacro{RPN}{Region Proposal Network}
\newacro{SIFT}{Scale Invariant Feature Transform}
\newacro{SVM}{Support Vector Machine}

@@

\begin{document}
% overall list of remaining stuff
%TODO figures: commas => dots
%TODO anonymize review version
%TODO denote dataset as work in progress and training version as 'v1.0'

@@

\abstract{
%%TODO write text here, 70-200 words
Current logo retrieval research focuses on closed set scenarios. We argue that the logo domain is too large for this strategy and requires an open set approach. To foster research in this direction, the large-scale Logos in the Wild dataset is collected and released to the public.
Searching for logos in image data has many applications, with judging the effectiveness of advertisement in sports event broadcasts being one example. Given a query sample in shape of a logo image, the task is to find all further occurrences of this logo in a database of images or videos. Currently, common logo retrieval approaches are unsuitable for this task because of their closed world assumption. To address this issue, an open set logo retrieval method is proposed in this work which allows searching for previously unfamiliar logos only by one query sample. A two stage concept with an open set logo detection and comparison is proposed. Both modules are based on task specific \acp{CNN}. The novel Logos in the Wild dataset serves to train the modules with sufficient appropriate in-the-wild data. 
The proposed method extends the application field in comparison to closed set approaches and significant improvements over baseline methods derived from these state-of-the-art closed set approaches are shown. 
}

@@

% Detector Frameworks: Faster R-CNN~\cite{ren2015}, SSD~\cite{liu2016b}, Yolo~\cite{redmon2016}, ...
\subsection{Object Detector Frameworks}
Early detectors applied hand-crafted features, such as Haar-like features, combined with a classifier to detect objects in images \cite{viola2004}. 
Nowadays, deep learning methods surpass the traditional methods by a significant margin. In addition, they allow a certain level of object classification within the detector which is mostly used to simultaneously detect different object categories \cite{sermanet2013}. 
%The OverFeat framework uses sliding windows on multiple scales of the image and combines the \ac{CNN} features to detect objects and classify them. 
The YOLO detector \cite{redmon2015} introduces an end-to-end network for object detection and classification based on bounding box regressors for object localization. This concept is similarly applied by the Single Shot MultiBox Detector (SSD) \cite{liu2016b}. 
Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a \ac{RPN} to detect object candidates in the feature maps and classifies the candidate regions by a fully connected network. 
Improvements of the Faster R-CNN are the Region-based Fully Convolutional Network (R-FCN) \cite{jifengdai2016b}, which reduces inference time by an end-to-end fully convolutional network, and the Mask R-CNN \cite{he2017}, adding a classification mask for instance segmentation.
%
\begin{figure*}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 6.6cm 0cm 0cm, clip]{img/openset.pdf}%
\caption{Comparison of closed and open set logo retrieval strategy.}%
\label{fig:openClosedSet}
\end{figure*}%

@@

\section{\uppercase{Logo Detection}}
%\noindent- class agnostic detector \\
%- different base networks: VGG-CNN-M, VGG16
\noindent The current state-of-the-art approaches for scene retrieval create a global feature of the input image. This is achieved by either inferring from the complete image or by searching for key regions and then extracting features from the located regions, which are finally fused into a global feature \cite{torii2015,arandjelovic2016,kalantidis2016}. For logo retrieval, extraction of a global feature is counterproductive because it lacks discriminative power to retrieve small objects. Additionally, global features usually include no information about the size and location of the objects which is also an important factor for logo retrieval applications.

Therefore, we choose a two-stage approach consisting of logo detection and logo classification as figure~\ref{fig:openClosedSet} illustrates for the open set case. First, the logos have to be detected in the input image. 
Since currently almost only Faster R-CNNs~\cite{ren2015} are used in the context of logo retrieval, we follow this choice for better comparability and because it offers a straight forward baseline method.
Other state-of-the-art detector options, such as SSD \cite{liu2016b} or YOLO \cite{redmon2016}, potentially offer a faster detection at the cost of detection performance \cite{huang2016b}.

Detection networks trained for the currently common closed set assumption are unsuitable to detect logos in an open set manner. By considering the output brand probability distribution, no derivation about occurrences of other brands are possible. Therefore, the task raises the need for a generic logo detector, which is able to detect all logo brands in general.

\subsubsection*{Baseline}
\vspace*{-2.5mm}
Faster R-CNN consists of two stages, the first being a \ac{RPN} to detect object candidates in the feature maps and the second being classifiers for the candidate regions. While the second stage specifies on the trained brands, the \ac{RPN} will generate candidates that vaguely resemble any of the brands which is the case for many other logos. Thus, it provides an indicator whether a region of the image is a logo or not. The trained \ac{RPN} and the underlying feature extractor network are extracted and employed as a baseline open set logo detector.

\subsubsection*{Brand Agnostic}
\vspace*{-2.5mm}
The \ac{RPN} strategy is by no means optimal because it obviously has a bias towards the pre-trained brands and also includes a certain amount of false positives.
Therefore, another option to detect logos is suggested which we call the brand agnostic Faster R-CNN. It is trained with only two classes: background and logo. We argue that this solution which merges all brands into a single class yields better performance than the \ac{RPN} detector because of two reasons. 
First, in the second stage fully connected layers preceding the output layer serve as strong classifiers which are able to eliminate false positives.
Second, the bounding box regression layers better adapt the bounding boxes to the logos resulting in a more precise localization. 
%Third, the combination of \ac{RPN} and the fully connected classifiers shape a cascade of detectors similarly as in \cite{viola2004}. The \ac{RPN} counts for a weaker classifier, which is faster and allows more false positives. In combination, it is expected to have a lower false positive rate.

@@

\section{\uppercase{Logo Comparison}}
%TODO write text here
\noindent After a logo is detected in an image, a correspondence from the query set should be searched. In order to retrieve as much objects from the images as possible, the detectors should work with a high recall. Although, for difficult tasks like open-set logo detection, high recall values induce usually a lot of false positive possible object locations. These examples should be eliminated by appropriate classifier. However, in case of image retrieval the goal is not direct classification, but rather feature extraction of a found region. Thus, the features of the logos of all the query images and the search set should be collected. The retrieved feature vectors are then normalized and the similarities of them are calculated with cosine similarity.
For baseline method, a Faster R-CNN is utilized, trained as usual. During inference, instead of detecting and classifying directly from the class probabilities, first the logos will be detected by processing the output of the \ac{RPN}. Then, the class scores are used as discriminative feature for the underlying region. The feature vector of the query images are extracted from the complete image, since the logos fill the majority of these images.
Donahue et al. proposed \cite{donahue2015}, that convolutional networks can produce excellent descriptors of the input image, regardless of the absence of fine-tuning to the specific context of the image. For this purpose, a network is pretrained on very large datasets, after which it can be deployed for a broad set of computer vision problems. In our case, the networks were additionally fine-tuned with different amount of logo images.
The proposed logo retrieval system consists of a class agnostic logo detector and a feature extractor network. This setup is advantageous for the quality of the extracted features, because the complete network is only focused on a specific region.

@@

The collected Logos in the Wild dataset exceeds the size of all related logo datasets as shown in table~\ref{tab:logoDatasets}. Even the union of all related logo datasets contains significantly less brands and RoIs which makes Logos in the Wild a valuable large-scale dataset.
The annotation is still an ongoing process and further larger versions of the dataset are expected to be published in the future (??).
%
%Potential uses: 
%In this work, the dataset is mainly used for training purposes
%In addition to the simple use as training data,

@@

In all cases, the \acp{CNN} are trained until convergence. Due to the diversity of applied networks and differing dataset sizes, training settings are numerous and optimized in each case with the validation data. Convergence occurs after 1,000 to 80,000 training iterations with a batch-size between 1 for the Faster R-CNN detector and 32 for the VGG16 training. 
%Training duration depends on the architecture as well as the amount of training data.
%TODO write text here

\subsection{Detection}
%- train 3 different detectors: multi-class Faster R-CNN (maybe \ac{RPN}), single-class Faster R-CNN, single-class Faster R-CNN + own logos\\
%- test on FlickrLogos-32 => FROC plot\\
%- test first two detectors on own logo dataset => FROC plot\\
%- Example Detections\\
%%TODO write text here
As baseline, the state-of-the-art closed set logo retrieval method from~\cite{su2016} based on Faster R-CNN is employed and trained on the public portion of the training data.
It is naively adapted to open set detection by using the \ac{RPN} scores as detections. This skips the closed set classification part of the network which is trained on different logos than should be detected on the test set.
%Because of the closed set training strategy, only brands occurring in the training set are the final outcome of this detector. 
%Adaptation to open set detection of previously unseen logos is achieved by using the RPN scores before classification as detections.
%Because of the strict separation of train and test brands, and the closed set training strategy
%the RPN scores serve as detections.
The proposed logo detector is first trained on the same public data for comparison. All Faster R-CNN detectors are based on VGG16 network.
The results in figure~\ref{fig:detectionFroc} indicate that the proposed brand agnostic strategy is superior by a significant margin. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
\caption{Detection FROC curves for the FlickrLogos-32 test set.}%
\label{fig:detectionFroc}
\end{figure}%
%

@@

\subsubsection*{FlickrLogos-32}
\vspace*{-2.5mm}
In 10 iterations, each of the 10 FlickrLogos-32 train samples for each brand serves as query sample. This allows to assess the statistical significance of results similar to a 10-fold-cross-validation strategy. Figure~\ref{fig:classificationFroc} shows the FROC results for the trained networks including indicators for the standard deviation of the measurements. The detection identification rate denotes the amount of ground truth logos which are correctly detected and are assigned the correct brand.
While the baseline method is only able to find a minor amount of the logos, our best performing approach is able to correctly retrieve 25 percent of the logos if tolerating only one false alarm every 100 images.
As expected, the more recent network architectures provide better results. Also, including the \ac{LitW} data in the training yields a significant boost in performance. Specifically, the larger training dataset has a larger impact on the performance than a better network architecture. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 7.4cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
\caption{Detection+Classification FROC curves for the FlickrLogos-32 test set. Including dashed indicators for one standard deviation. DenseNet results are omitted for clarity, refer to table~\ref{tab:mapFlickr} for full results.}%
\label{fig:classificationFroc}
\end{figure}%
%
%As far as we are aware, this is the first experiment with open set logo retrieval on 
Table~\ref{tab:mapFlickr} compares our open set results with closed set results from the literature in terms of the mean average precision (\map). 
%
\begin{table}[t]
\centering
\begingroup	
\setlength{\tabcolsep}{6pt}
\caption{FlickrLogos-32 test set retrieval results.}
\label{tab:mapFlickr}
\begin{small}
% Table generated by Excel2LaTeX from sheet 'FlickrLogos-32Test'
\begin{tabular}{crc}
\textbf{setting} & \multicolumn{1}{c}{\textbf{method}} & \textbf{\map} \bigstrut[b]\\
\hline
\multirow{7}[2]{*}{\begin{sideways}open set\end{sideways}} & baseline, public~\cite{su2016} & 0.036 \bigstrut[t]\\
      & \textit{VGG16, public} & 0.286 \\
      & \textit{ResNet101, public} & 0.327 \\
      & \textit{DenseNet161, public} & 0.368 \\
\cline{2-3}      
      & \textit{VGG16, public+\ac{LitW}} & 0.382 \bigstrut[t]\\
      & \textit{ResNet101, public+\ac{LitW}} & \textbf{0.464} \\
      & \textit{DenseNet161, public+\ac{LitW}} & 0.448  \bigstrut[b]\\      
\hline
\multirow{4}[1]{*}{\begin{sideways}closed set\end{sideways}} & BD-FRCN-M \cite{oliveira2016} & 0.735 \bigstrut[t]\\	
      & DeepLogo \cite{iandola2015} & 0.744 \\ 
      & Faster-RCNN \cite{su2016} & 0.811 \\
      & Fast-M \cite{bao2016} & \textbf{0.842} \\
\end{tabular}%
\end{small}
\endgroup
\end{table}
We achieve more than half of the closed set performance in terms of \map~with only one sample for a brand at test time instead of dozens or hundreds of brand samples at training time. In addition, our approach is not limited to the 32 FlickrLogos brands but generalizes with a similar performance to further brands. In contrast, the closed-set approaches hardly generalize as is shown by the baseline open set method. This is the second best closed set approach only retrained on out-of-test brands.

\subsubsection*{SportsLogos}
\vspace*{-2.5mm}
In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events. In total, this SportsLogos test set includes 298 annotated frames with 2,348 logos of 40 brands. In comparison to public logo datasets, the logos are usually significantly smaller in these cases and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}. Besides perimeter advertising, logos on clothing or equipment of the athletes and TV station or program overlays are the most occurring logo types.
Overall, the results in this application scenario are slightly worse than in the FlickrLogos-32 benchmark with a drop in \map~from 0.464 to 0.354 for the best performing method, as indicated in figure~\ref{fig:classificationFrocFootball}. The baseline approach takes the largest performance hit showing that closed set approaches not only generalize badly to unseen logos but also to novel domains. In contrast, the proposed open set strategy shows a relatively stable cross-domain performance. Training with \ac{LitW} data again improves the results significantly.
%
\begin{figure*}%
\centering%
\includegraphics[width=\linewidth]{img/football-1908719_1920_cut.jpg}%
\caption{Example football scene with small logos in the perimeter advertising.}%
\label{fig:footballSample}
\end{figure*}%
%
%Due to copyright reasons this internal dataset cannot be made publicly available.
%
%\begin{table}[t]
%\centering
%\begingroup	
%\setlength{\tabcolsep}{5pt}
%\caption{SportsLogos dataset statistics.}
%\label{tab:sportDataStatistics}
%\begin{small}
%\begin{tabular}{l|cccc}
% & \textbf{phase} & \textbf{brands} & \sizebox{1.0cm}{\textbf{logo images}} & \textbf{RoIs} \bigstrut[b]\\
%\hline
%football-1 & \multirow{3}{*}{train} & {104} & {331} & {3,329} \bigstrut[t]\\
%{ski} & & {27} & {179} & {701} \\
%{ice hockey} & & {19} & {410} & {3,920} \bigstrut[b]\\
%\hline
%{football-2} & test & 40 & 298 & 2,348 \bigstrut\\
%%\hline
%%{total} & & {143 (union)} & {1,218} & {10,298} \bigstrut[t]\\
%\end{tabular}
%\end{small}
%\endgroup
%\end{table}
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 8.5cm 0cm 0cm, clip]{img/classificationFrocFootball.pdf}%
\caption{Detection+Classification FROC curves for the Sports\-Logos test set, \map~is given in brackets.}%
\label{fig:classificationFrocFootball}
\end{figure}%
%
